Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-27 Moltres.tex
Add mesh convergence to Moltres.tex.

The model molten salt reactor closely emulates the \gls{MSRE}. When developing new physics or investigating
different types of transients, one can reduce the model problem to a two
dimensional axisymmetric one for rapid proof of concept. To approximately simulate the lattice
structure of the \gls{MSRE} under 2D conditions, a geometry is constructed with 14 repeating
fuel-moderator regions, as shown in \Cref{fig:geom}. The fuel and moderator
radii are chosen such that the resulting area/volume fraction of fuel is 0.225 as
for the \gls{MSRE}.

>>>>

The model molten salt reactor closely emulates the \gls{MSRE}. When developing new physics or investigating
different types of transients, one can reduce the model problem to a two
dimensional axisymmetric one for rapid proof of concept. To approximately simulate the lattice
structure of the \gls{MSRE} under 2D conditions, a geometry is constructed with 14 repeating
fuel-moderator regions, as shown in \Cref{fig:geom}. The fuel and moderator
radii are chosen such that the resulting area/volume fraction of fuel is 0.225 as
for the \gls{MSRE}. The 2D mesh has a characteristic size of 10 cm in the axial
direction and .4 cm in the radial direction to capture the variation from moving
between fuel and moderator subdomains. Solution time on the resulting 1960
element, 8697 DOF problem is a couple minutes on a single core. Solving on a
mesh uniformly refined three times yields the same qualitative behavior
described in the results that follow for the coarse mesh. Additionally the 3x
refinement yielded only a 1 K change in the average reactor temperature; thus,
the coarse mesh results are regarded as sufficiently converged.
